---
html_document: default
author: "Harry Woo"
date: "2020-5-18"
output:
  word_document: default
  latex_engine: xelatex
  pdf_document: null
  html_document:
    df_print: paged
mainfont: NanumGothic
html_notebook: default
title: "Faraway Ch14"
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

이 과제물은 1차적으로 R Markdown 으로 작성되었으며, Word 문서로 knit 후 가독성을 위하여 일부 내용을 추가로 편집하였습니다.


## Faraway Chapter 14 Categorical Predictors
### Problem 1

_Using the teengamb data, model gamble as the response and the other variables as predictors, investigate the possibility of interactions between sex and the other predictors. Interpret your final model._

```{r load packages, message=FALSE, warning=FALSE, include=TRUE}

library(faraway)
library(ggplot2)
library(dplyr)
library(knitr)
library(pander)
library(gt)
library(officer)
library(flextable)
library(ellipse) 
library(purrr)
library(GGally)
library(MASS)
library(car)
library(tibble)
library(gridExtra)

```


#### model fitting
`gamble`를 종속변수로, 다른 변수를 설명변수로 하여 회귀모형 `tg_lm`을 적합하였다.

```{r teengamb-model-fitting}

data(teengamb)
head(teengamb)
?teengamb

tg <- teengamb %>% 
  mutate(sex = factor(sex, labels = c("male", "female")))

ggpairs(tg, legend = 1, 
        mapping = aes(colour = sex),
        lower = list(continuous = wrap("smooth", alpha = 0.3, size = 0.1)),
        diag = list(discrete="barDiag", 
                    continuous = wrap("densityDiag", alpha = 0.5 )),
        upper = list(combo = wrap("box_no_facet", alpha = 0.5),
                            continuous = wrap("cor", size = 4,
                                              alignPercent = 0.8))) +
  theme(legend.position = "bottom")

```

```{r}

tg_lm <- lm(gamble ~ sex + status + income + verbal, data = tg)
summary(tg_lm)
shapiro.test(tg_lm$residuals)

tg2 <- tg %>% 
  mutate(gamble = ifelse(gamble == 0, gamble + 0.1, gamble))

tg2_lm <- lm(log(gamble) ~ sex + status + income + verbal, data = tg2)
summary(tg2_lm)
plot(tg2_lm)
shapiro.test(tg2_lm$residuals)

tg2_lm2 <- lm(log(gamble) ~ sex + status + log(income) + verbal, data = tg2)
summary(tg2_lm2)
plot(tg2_lm2)
shapiro.test(tg2_lm2$residuals)

```


#### interactions

```{r teengamb-interactions}

inter1 <- ggplot(data = tg2, aes(x = income, y = gamble, colour = sex)) +
  geom_point() + stat_smooth(method = lm, fullrange = TRUE, se = TRUE) +
  theme(legend.position = "bottom")
inter2 <- ggplot(data = tg2, aes(x = status, y = gamble, colour = sex)) +
  geom_point() + stat_smooth(method = lm, fullrange = TRUE, se = TRUE) +
  theme(legend.position = "bottom")
inter3 <- ggplot(data = tg2, aes(x = verbal, y = gamble, colour = sex)) +
  geom_point() + stat_smooth(method = lm, fullrange = TRUE, se = TRUE) +
  theme(legend.position = "bottom")
grid.arrange(inter1, inter2, inter3, ncol = 3, top = "Finding interactions by sex")


tg2_lm3 <- lm(log(gamble) ~ sex + status + log(income) + verbal + 
                sex*status + sex*log(income) + sex*verbal, data = tg2)
summary(tg2_lm3)
plot(tg2_lm3)
shapiro.test(tg2_lm3$residuals)


tg2_lm4 <- lm(log(gamble) ~ sex*status + sex*income + sex*verbal, data = tg2)
summary(tg2_lm4)
plot(tg2_lm4)
shapiro.test(tg2_lm4$residuals)


```


#### final model

https://www.rpubs.com/amnshhbddn/267915
https://rstudio-pubs-static.s3.amazonaws.com/267915_44a89940b5754134b1573afad335a70c.html#exercise-3-teengamb-gambling-data
http://www.utstat.utoronto.ca/reid/sta2201s/2012/hw3soln.pdf
https://stat.ethz.ch/education/semesters/as2011/asr/Uebungen/solution3.pdf
https://github.com/peach07up/stat420/blob/master/hw12/420Hw06ans.pdf

skewed 를 고려하여 Log를 취한 모형이 설명력은 떨어지나 diagnosis에서 문제가 없어


### Problem 2

_Plot the ToothGrowth data with len as the response. Fit a linear model to the data and check for possible simplification. Display the fitted regression lines on top of the data._

#### model fitting
`len`를 종속변수로, 다른 변수를 설명변수로 하여 회귀모형 `tg_lm`을 적합하였다.

```{r -model-fitting}

data(ToothGrowth)
head(ToothGrowth)

str(ToothGrowth)
table(ToothGrowth$supp)
table(ToothGrowth$dose)
?ToothGrowth

pig_lm <-  lm(len ~ supp + dose, data = ToothGrowth)
summary(pig_lm)

ggpairs(ToothGrowth, mapping = aes(colour = supp),
        lower = list(continuous = wrap("smooth", alpha = 0.3, size = 0.1)),
        diag = list(discrete="barDiag", 
                    continuous = wrap("densityDiag", alpha = 0.5 )),
        upper = list(combo = wrap("box_no_facet", alpha = 0.5),
                            continuous = wrap("cor", size = 4,
                                              alignPercent = 0.8))) +
  theme(legend.position = "bottom")

ggplot(data = ToothGrowth, aes(x = dose, y = len, colour = supp))+
  geom_point() + stat_smooth(method = lm, fullrange = TRUE, se = TRUE)


```

```{r}

pig_lm2 <- lm(len ~ supp*dose, data = ToothGrowth)
summary(pig_lm2)

pig_lm2_step <- stepAIC(pig_lm2, direction = "back")
pig_lm2_step$anova

prediction <- data.frame(len_pred = predict(pig_lm2, data = ToothGrowth))

ToothGrowth2 <- ToothGrowth %>% 
  mutate(len_pred = predict(pig_lm2, data = ToothGrowth))

pred_conf <- predict(pig_lm2, data = ToothGrowth, interval = "confidence")

ToothGrowth2 <- cbind(ToothGrowth2, pred_conf)

ggplot(data = ToothGrowth2, aes(x = dose, y = len, colour = supp))+
  geom_point() + 
  geom_ribbon(aes(ymin = lwr, ymax = upr, fill = supp, colour=NULL), alpha = 0.1) +
  geom_line(aes(x = dose, y = len_pred), size = 1)




```

http://rstudio-pubs-static.s3.amazonaws.com/36933_2f77a95d4d1e47df81c1dd5047e61016.html

https://rpubs.com/akonkel/ToothGrowth


### Problem 3

_Find a good model for the uswages data with wages as the response and all the other variables as predictors._

http://rstudio-pubs-static.s3.amazonaws.com/316501_10093f3aaff0490ca23c8bd3404185fc.html

```{r ch14-3-EDA}

data(uswages)
head(uswages)

str(uswages)
summary(uswages)
sum(!complete.cases(uswages)) #결측치 확인

```

```{r ch14-3-NA}

uswages2 <- uswages %>% 
  rownames_to_column() %>% 
  mutate(exper = ifelse(exper < 0, NA, exper))

head(uswages2)

sum(is.na(uswages2$exper))
uswages2 <- na.omit(uswages2)
nrow(uswages2)

```

```{r ch14-3-factor}

uswages2 %>% 
  mutate(area_sum = ne + mw + we + so) %>% 
  dplyr::select(area_sum) %>% 
  table()

uswages2 <- uswages2 %>% 
  mutate(race = factor(race, labels = c("White", "Black")),
         smsa = factor(smsa, labels = c("No", "Yes")),
         area_temp = 1*ne + 2*mw + 3*we + 4*so,
         area = factor(area_temp, labels = c("ne", "mw", "we", "so")),
         pt = factor(pt, labels = c("No", "Yes"))) %>% 
  dplyr::select(-c("ne", "mw", "we", "so","area_temp"))

summary(uswages2)
str(uswages2)

uswages2 %>% 
  mutate(wage = log(wage)) %>% 
  dplyr::select(-"rowname") %>% 
  ggpairs()

```

```{r 14-3-lm1}

wage_lm <- lm(wage ~ educ + exper + race + smsa + pt + area, data = uswages2)
summary(wage_lm)
plot(wage_lm)

```


```{r 14-3-lm2}

wage_lm2 <- lm(log(wage) ~ educ + exper + race + smsa + pt + area, data = uswages2)
summary(wage_lm2)
plot(wage_lm2)

```

```{r ch14-3-res}

uswages3 <- uswages2[-c(1545, 1017, 1550),]
wage_lm3 <- lm(log(wage) ~ educ + exper + race + smsa + pt + area, data = uswages3)
summary(wage_lm3)
plot(wage_lm3)

shapiro.test(residuals(wage_lm3))
plot(cooks.distance(wage_lm2))

step <- stepAIC(wage_lm2, direction = "both")
step$anova

step <- stepAIC(wage_lm3, direction = "both")
step$anova

wage_lm4 <- lm(log(wage) ~ educ + exper + race + smsa + pt, data = uswages3)
summary(wage_lm4)
plot(wage_lm4)

plot(x = uswages2$area, y = uswages2$wage, ylim = c(0, 3000))

summary(lm(log(wage) ~ educ + exper + race + smsa + pt + area2, data = uswages3))

vif(wage_lm2)

```


http://rstudio-pubs-static.s3.amazonaws.com/316504_1d7d88789c08404096c69a20783ae481.html

