---
title: "Final_Assignment"
author: "Harry Woo"
date: '2020 5 26 '
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Problem 1

_Chapter 12 Chicago Insurance Redlining- a complete example in Faraway-PRA 의 주요 기본 분석 처리를 Rstudio의 rmarkdown 을 이용하여 html(또는 pdf) 요약보고서로 간단히 정리하여 제출하기_



### Problem 2

https://socialsciences.mcmaster.ca/jfox/Courses/SPIDA/
https://sms.wgtn.ac.nz/foswiki/pub/Courses/DATA303_2020T1/Lab2/lab2.html
https://sms.wgtn.ac.nz/foswiki/pub/Courses/DATA303_2020T1/Lab3/lab3.html
https://sms.wgtn.ac.nz/foswiki/pub/Courses/DATA303_2020T1/Lab4/lab4.html
http://www.jpstats.org/Regression/ch_05_05.html

_After exploring the data graphically, perform a linear least‐squares regression of the total fertility rate (`tfr`) on GDP per capita (`GDPperCapita`), the female illiteracy rate (`illiteracyFemale`), and the rate of contraceptive use by married women (`contraception`)._

_Introduce the factor `region` into the regression, first fitting an additive model to the data and then considering the possibility that region interacts with the other explanatory variables._

#### 2.0 Data loading

```{r}

UN <- read.table("http://socialsciences.mcmaster.ca/jfox/Books/Applied-Regression-2E/datasets/UnitedNations.txt", header = TRUE)

```

#### 2.1 Exploring the data graphically

```{r}



```


#### 2.2 Linear least-squares regression

```{r}



```

#### 2.3 Introducing the factor `region`

```{r}



```

##### 2.3.1 Fitting and additive model

```{r}



```

##### 2.3.2 Considering the possibility that region interacts with the other

```{r}



```

solution by Fox

UN <- read.table("http://socserv.mcmaster.ca/jfox/Books/Applied-Regression-2E/datasets/UnitedNations.txt", header=TRUE) 
UN <- na.omit(UN[,c("tfr", "GDPperCapita", "illiteracyFemale", "contraception", "region")]) 

mod1 <- lm(tfr ~ GDPperCapita + illiteracyFemale + contraception, data=UN) 
summary(mod1) 

library(car) 
qq.plot(mod1) 
rstud <- rstudent(mod1) 
plot(density(rstud)) 
boxplot(rstud) 
identify(rep(1, length(rstud)), rstud, names(rstud)) 
influencePlot(mod1) 
av.plots(mod1, ask=FALSE) 
cr.plots(mod1, ask=FALSE) 
mod2 <- lm(tfr ~ log(GDPperCapita) + logit(illiteracyFemale) + contraception, data=UN) summary(mod2) 
cr.plots(mod2, ask=FALSE) 
qq.plot(mod2) 
rstud <- rstudent(mod2) 
plot(density(rstud)) 
boxplot(rstud) 
identify(rep(1, length(rstud)), rstud, names(rstud)) 
influencePlot(mod2) 
av.plots(mod2, ask=FALSE) 
mod3 <- lm(tfr ~ log(GDPperCapita) + logit(illiteracyFemale) + contraception + region, data=UN) 
summary(mod3) 
Anova(mod3) 
cr.plots(mod3, ask=FALSE) 
influencePlot(mod3) 
qq.plot(mod3) 
rstud <- rstudent(mod3) 
plot(density(rstud)) 
boxplot(rstudent(mod3)) 
identify(rep(1, length(rstud)), rstud, names(rstud)) 
mod4 <- lm(tfr ~ (log(GDPperCapita) + logit(illiteracyFemale) + contraception)*region, data=UN) 
Anova(mod4) 
mod5 <- lm(tfr ~ log(GDPperCapita) + logit(illiteracyFemale) + contraception*region, data=UN) 
Anova(mod5) 
library(effects) 
plot(allEffects(mod5, default.levels=100), ask=FALSE) 


### Problem 3

_Using the Canadian occupational prestige data (the Prestige data frame in the car package – see ?Prestige), replicate the linear regression of prestige on education, income, and women (i.e., percent women in the occupation)._

_Use “regression diagnostics” to check for problems in this regression and attempt to correct any problems that you discover._

```{r}

library(car)
data("Prestige")

head(Prestige)

```

solution by Fox

library(car) 
modp1 <- lm(prestige ~ income + education + women, data=Prestige) 
summary(modp1) 
qq.plot(modp1, simulate=TRUE, line="none") 
rstud <- rstudent(modp1) 
plot(density(rstud)) 
boxplot(rstud) 
influencePlot(modp1) 
av.plots(modp1, ask=FALSE)
cr.plots(modp1, ask=FALSE) 
modp2 <- lm(prestige ~ log10(income) + education + poly(women, 2), data=Prestige) 
summary(modp2) 
Anova(modp2) 
influencePlot(modp2) 
cr.plots(modp2, ask=FALSE) 

